The population of long-period exoplanets I. --- \\ Fully-automated discovery \& characterization of long-period transiting exoplanet candidates in the \kepler\ archive

### 2016-02-27 document/ms.tex
nothin

For up to three candidate transit times per light curve, we select a
contiguous chunk of light curve approximately centered on the proposed transit
with no more than 500 cadences \dfmtodo{check me} and compute the BIC of each
model for this data set.
We will define the BIC for a model $k$ in the set of $K$ models is given by
\begin{eqnarray}
\mathrm{BIC}_k &=& \ln \mathcal{L}^* - \frac{J}{2}\,\log N
\end{eqnarray}
where the likelihood function $\mathcal{L}$ is evaluated at its maximum, $J$
is the number of free parameters in the model, and $N$ is the number of
data points in the data set.

>>>>

For up to three candidate transit times per light curve, we select a
contiguous chunk of PDC light curve approximately centered on the proposed
transit with no more than 500 cadences \dfmtodo{check me} and compute the BIC
of each model for this data set.
We will define the BIC for a model $k$ in the set of $K$ models is given by
\begin{eqnarray}
\mathrm{BIC}_k &=& \ln \mathcal{L}^* - \frac{J}{2}\,\log N
\end{eqnarray}
where the likelihood function $\mathcal{L}$ is evaluated at its maximum, $J$
is the number of free parameters in the model, and $N$ is the number of
data points in the data set.
